### 2020-10-14 Thesis-Chapter2-Background.tex
Update title and README
Update outline and renumber regulations sections

The following sections list laws which directly or indirectly affect use of encryption. Though this thesis is
U.S.--focused, it is worth briefly touching on the regulatory environment of other countries. \Ac{EA} is an
international problem, as digital technology has little respect for political borders.

@@

\subsection{U.S. Efforts to Regulate Encryption}

This section includes both successful and failed cryptography regulation attempts in the U.S.

\subsubsection{Enacted U.S. Regulations}

@@

\subsubsection{Unsuccessful U.S. Regulation Attempts}
\label{sec-us-reg-fails}

@@

\subsubsection{The Judicial Environment}
\label{sec-us-judicial}

@@

The primary judiciary function is to adjudicate the law through the determination of facts and interpretation of
authoritative legal texts. However, whether it is condemned, denied, seen as a stark reality, or seen as a valid
function, the judicial branch also establishes legal doctrine and actively enforces rulings in a manner that amounts to
creation of public policy \cite{feeley_judicial_2000}. Due to the clear congressional authority over telecommunications
and federal investigatory powers, the courts are most likely to exert influence in this area through interpretation of
current law. This interpretation will both determine how present law is enforced and draw a constitutional fence around
any actions the executive or legislative branches undertake.

@@

\subsection{Regulations around the World}

@@

In some cases, a suspect in custody may have the ability to access the desired encrypted information via a key,
\ac{PIN}, or password. In these cases, authorities sometimes compel the suspect to disclose the password. In the U.S.,
this approach draws debates about the fifth amendment right against self-incrimination \cite{bittenbender_2019}
\cite{sobel_2019}. Of course, this approach cannot address \ac{DIM} or situations in which the knowledgeable party is
not in custody.

>>>>

The following sections list laws which directly or indirectly affect use of encryption. Though this thesis is
U.S.--focused, it is worth briefly touching on the regulatory environment of other countries. \Ac{EA} is an
international problem, as digital technology has little respect for political borders.
\mysecrange{sec-us-regs}{sec-us-judicial} describe the regulatory environment in the U.S. and \mysec{sec-world-regs}
describes regulations around the world.

@@

\subsection{Enacted U.S. Regulations}
\label{sec-us-regs}

@@

\subsection{Unsuccessful U.S. Regulation Attempts}
\label{sec-us-reg-fails}

@@

\subsection{The U.S. Judicial Environment}
\label{sec-us-judicial}

@@

The primary judiciary function is to adjudicate the law through the determination of facts and interpretation of
authoritative legal texts. However, whether it is condemned, denied, seen as a stark reality, or seen as a valid
function, the judicial branch also establishes legal doctrine and actively enforces rulings in a manner that amounts to
creation of public policy \cite{feeley_judicial_2000}. Due to the clear congressional authority over telecommunications
and federal investigatory powers, the courts are most likely to exert influence in this area through interpretation of
current law. This interpretation will both determine how present law is enforced and draw a constitutional line around
any actions the executive or legislative branches undertake.

@@

% Prof. Walsh:
% Due to the dynamic nature of future judicial rulings that may expand or retract the application of exceptional access
% it is beyond the scope of this research to comment further...

\subsection{Regulations around the World}
\label{sec-world-regs}

@@

In some cases, a suspect in custody may have the ability to access the desired encrypted information via a key,
\ac{PIN}, or password. In these cases, authorities sometimes compel the suspect to disclose the password. In the U.S.,
this approach draws debates about the Fifth Amendment right against self-incrimination \cite{bittenbender_2019}
\cite{sobel_2019}. Of course, this approach cannot address \ac{DIM} or situations in which the knowledgeable party is
not in custody.
